---
title: "Homework 5"
author: Ziyan Xu
date: 11/10/2022
output: 
  github_document:
    toc: true
---

This is my solution to HW5. 

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d()
scale_fill_discrete = scale_fill_viridis_d()
```

### Problem 1



### Problem 2

#### Load and describe the raw dataset

```{r include = FALSE}
raw_df = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

This dataset contains `r nrow(raw_df)` rows and `r ncol(raw_df)` columns.

The data contains the location of the killing, whether an arrest was made, basic demographic information of each victim. There are victim info variables -- victim_last, victim_first, victim_race, victim_age and victim_sex, location variables -- city, state, lat and lon, and case info -- uid, reported_date and disposition.

#### Clean the dataset
```{r echo = FALSE, message = FALSE}
homicide_df = 
  raw_df %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")) %>% 
  filter(city_state != "Tulsa, AL") %>% 
  relocate(city_state) %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    total = n())
homicide_df
```

#### Proportion of unsolved homicides

Run `prop.test` for Baltimore, MD.
```{r}
baltimore_summary = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
baltimore_test =
  prop.test(
    pull(baltimore_summary, unsolved), 
    pull(baltimore_summary, total)) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))
baltimore_test
```

Run `prop.test` for each city.
```{r}
homicide_cities =
  homicide_df %>%
  mutate(
    test_results = map2(unsolved, total, prop.test),
    tidy_results = map(test_results, broom::tidy)) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
homicide_cities
```

Scatterplot showing the estimates and CIs for each city.

```{r, dpi = 300, echo=FALSE}
homicide_cities %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate, color = city_state)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "none") +
  labs(
    x = "City",
    y = "Estimated Proportion of Unsolved Homicides",
    title = "Estimated Proportion of Unsolved Homicides in Each City"
  )
```

### Problem 3

